---
title: "Stats 101C Project"
author: "Hayley Todd"
output: html_document
---

```{r}
setwd("~/Downloads")
project <- read.csv("HTrainLast.csv")
projecttest <- read.csv("HTestLastNoY.csv")
sum(complete.cases(project))
head(projecttest)
sapply(project,function(x) sum(is.na(x)))
```


```{r}
head(projecttest)
projecttest <- projecttest[,-1]
library(tidyr)
library(dplyr)
trialtest <- projecttest %>% distinct()
dim(trialtest)
```

```{r}
attach(project)
levels(Alley) <- c(levels(Alley), "None")
Alley[is.na(Alley)] <- "None"
project$Alley <- Alley

levels(BsmtCond) <- c(levels(BsmtCond), "None")
BsmtCond[is.na(BsmtCond)] <- "None"
project$BsmtCond <- BsmtCond

levels(BsmtExposure) <- c(levels(BsmtExposure), "None")
BsmtExposure[is.na(BsmtExposure)] <- "None"
project$BsmtExposure <- BsmtExposure

levels(BsmtQual) <- c(levels(BsmtQual), "None")
BsmtQual[is.na(BsmtQual)] <- "None"
project$BsmtQual <- BsmtQual

levels(BsmtFinType1) <- c(levels(BsmtFinType1), "None")
BsmtFinType1[is.na(BsmtFinType1)] <- "None"
project$BsmtFinType1 <- BsmtFinType1

levels(BsmtFinType2) <- c(levels(BsmtFinType2), "None")
BsmtFinType2[is.na(BsmtFinType2)] <- "None"
project$BsmtFinType2 <- BsmtFinType2

levels(FireplaceQu) <- c(levels(FireplaceQu), "None")
FireplaceQu[is.na(FireplaceQu)] <- "None"
project$FireplaceQu <- FireplaceQu

levels(GarageType) <- c(levels(GarageType), "None")
GarageType[is.na(GarageType)] <- "None"
project$GarageType <- GarageType

levels(GarageFinish) <- c(levels(GarageFinish), "None")
GarageFinish[is.na(GarageFinish)] <- "None"
project$GarageFinish <- GarageFinish

levels(GarageQual) <- c(levels(GarageQual), "None")
GarageQual[is.na(GarageQual)] <- "None"
project$GarageQual <- GarageQual

levels(GarageCond) <- c(levels(GarageCond), "None")
GarageCond[is.na(GarageCond)] <- "None"
project$GarageCond <- GarageCond

project$GarageYrBlt <- as.factor(GarageYrBlt)

levels(PoolQC) <- c(levels(PoolQC), "None")
PoolQC[is.na(PoolQC)] <- "None"
project$PoolQC <- PoolQC

levels(Fence) <- c(levels(Fence), "None")
Fence[is.na(Fence)] <- "None"
project$Fence <- Fence

levels(MiscFeature) <- c(levels(MiscFeature), "None")
MiscFeature[is.na(MiscFeature)] <- "None"
project$MiscFeature <- MiscFeature

MSSubClass <- as.factor(MSSubClass) ##Makes it so that the numbers are categories
project$MSSubClass <- MSSubClass


dim(project)
sum(complete.cases(project))
sapply(project,function(x) sum(is.na(x)))
nolotproject <- project[,-4]
head(nolotproject)
sapply(nolotproject,function(x) sum(is.na(x)))
nolotprojcomp <- nolotproject[which(complete.cases(nolotproject)),]
dim(nolotprojcomp)
3451/3500

fullproj <- project[which(complete.cases(project)),]
write.csv(fullproj, file = "cleanproject83.csv")
write.csv(project, file = "cleanprojectfull.csv")
write.csv(nolotprojcomp, file = "cleannolotcomp.csv")

detach(project)
attach(fullproj)
head(fullproj)
dim(fullproj)
```

```{r}
library(dplyr)
which(is.na(project$affordabilitty) == T)
project <- project[-c(833,2428),]
dim(project)
sapply(fullproj,function(x) sum(is.na(x)))
summary(project$LotFrontage)
```

```{r}
project$Utilities[c(2326,3380)] <- "AllPub"
project$BsmtFullBath[c(2074,2847)] <- 0
project$BsmtHalfBath[c(2074,2847)] <- 0
```

```{r}
which(complete.cases(project$KitchenQual) == FALSE)
project[c(1458,2735),] #these are identical

project$KitchenQual <- as.character(project$KitchenQual)

kitchensub <- project[which(complete.cases(project$KitchenQual)==TRUE),]
kitchensub <- kitchensub[which(kitchensub$KitchenAbvGr == 1),]
dim(kitchensub)

junkkitchen <- kitchensub$KitchenQual
#junkkitchenrooms <- project$KitchenAbvGr[which(complete.cases(project$KitchenQual)==TRUE)]

length(junkkitchen)
newkitchqual <- numeric(3335)
for(i in 1:length(junkkitchen)){
  if(junkkitchen[i] == "Ex"){
    newkitchqual[i] = 5
  }
  if(junkkitchen[i] == "Gd"){
    newkitchqual[i] = 4
  }
  if(junkkitchen[i] == "TA"){
    newkitchqual[i] = 3
  }
  if(junkkitchen[i] == "Fa"){
    newkitchqual[i] = 2
  }
  if(junkkitchen[i] == "Po"){
    newkitchqual[i] = 1
  }
}

kitchenstuff <- data.frame(kitchensub$KitchenAbvGr,newkitchqual)
head(kitchenstuff)
median(kitchenstuff$newkitchqual)
project$KitchenQual[c(1458,2735)] <- "TA"
project$KitchenQual <- as.factor(project$KitchenQual)

levels(project$KitchenQual)
```

```{r}
summary(project$Functional)
which(complete.cases(project$Functional) == FALSE)
project[c(112,2766,3152),] #112 and 2766 are identical
##Data description says "Assume typical unless deductions are warranted" so will fill in NAs with Typ
project$Functional[c(112,2766,3152)] <- "Typ"
```

```{r}
summary(project$Electrical)
which(complete.cases(project$Electrical) == FALSE)
project[c(849,2417),] #identical
library(ggplot2)
ggplot(project, aes(x = YearBuilt, fill = Electrical)) + geom_density(alpha = 0.5) + labs(title = "Density of Year Built By Electrical Type") + theme(plot.title = element_text(hjust =  0.5))
project$Electrical[c(849,2417)] <- "SBrkr"
```


```{r}
sapply(project,function(x) sum(is.na(x)))
```
MSZoning (factor of 5 variables) 4 missing, Lot Frontage (numerical), MasVnrType and MasVnrArea (these missing values should be the same) (type is factor, area is numerical) (NA type has an area)

```{r}
numbers <- which(complete.cases(project$MasVnrType) == FALSE)
which(complete.cases(project$MasVnrArea) == FALSE) #2894 has type but no area
##5,111,122 are identical

project[5,]==project[111,]
project[numbers,]

project[2894,]
MasVnrmod <- lm(MasVnrArea ~ MasVnrType, data = project)
summary(MasVnrmod)
```

```{r}
which(complete.cases(project$MSZoning) == FALSE)
project[c(47,112,2326,2766),]
```

removing duplicate rows based on all columns:
THIS IS WHERE NEWCLEANFULL IS MADE!!

```{r}
head(project)
trialproj <- project[,-1]
trialproj$KitchenQual[c(1458,2735)] <- "TA"
trialproj$KitchenQual <- as.factor(trialproj$KitchenQual)
levels(trialproj$KitchenQual)
projnorepeat <- trialproj %>% distinct()
dim(projnorepeat)
sapply(projnorepeat,function(x) sum(is.na(x)))
## NEW CLEAN FULL
write.csv(trialproj, file = "newcleanfull.csv")
#write.csv(projnorepeat, file = "norepeatdata.csv")
```


```{r}
detach(fullproj)
set.seed(97531739)
train <- sample(1:dim(fullproj)[1], dim(fullproj)[1]*0.7)
traintrain <- fullproj[train,]
testtrain <- fullproj[-train,]

Affordable <- fullproj[fullproj$affordabilitty == "Affordable",]
Unaffordable <- fullproj[fullproj$affordabilitty == "Unaffordable",]
```

```{r}
ggplot(project, aes(x = MasVnrType, y = MasVnrArea, fill = MasVnrType)) + geom_boxplot()
```

```{r}
View(data.frame(project$MasVnrType, project$MasVnrArea))
```


Fancier graph attempts:

MSSubClass

```{r}
ggplot(trialproj, aes(x = MSSubClass, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

MSZoning:
```{r}
ggplot(trialproj, aes(x = MSZoning, fill = affordabilitty)) + geom_bar(position = position_dodge())
#ggplot(projnorepeat, aes(x = MSZoning, fill = affordabilitty)) + geom_bar(position = position_dodge())
```


Lot info:
```{r}
attach(fullproj)
library(ggplot2)

par(mfrow=c(1,2))
ggplot(trialproj, aes(x = LotFrontage, fill = affordabilitty)) + 
  geom_density(alpha = 0.5) #No
ggplot(projnorepeat, aes(x = LotFrontage, fill = affordabilitty)) + 
  geom_density(alpha = 0.5) #No
```
```{r}
ggplot(trialproj, aes(x = affordabilitty, y = log(LotArea), fill = affordabilitty)) + 
  geom_boxplot(alpha = 0.5) + 
  coord_flip() + labs(title = "Log of Lot Area Based on Affordability") + theme(plot.title = element_text(hjust = 0.5))

```

```{r}
ggplot(fullproj, aes(x = log(LotArea), fill = affordabilitty)) + geom_density(alpha = 0.5)
```

Street:
```{r}
ggplot(trialproj, aes(x = Street, fill = affordabilitty)) + geom_bar(position = position_dodge())

ggplot(projnorepeat, aes(x = Street, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

Alley:
```{r}
ggplot(trialproj, aes(x = Alley, fill = affordabilitty)) + geom_bar(position = position_dodge())
#junkmod <- glm(affordabilitty ~ Alley, data = fullproj, family = 'binomial')
#summary(junkmod)
```

```{r}
gravel <- c(which(new.test$Alley == "Grvl"))
```


LotShape:
```{r}
ggplot(trialproj, aes(x = LotShape, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

LandContour:
```{r}
ggplot(trialproj, aes(x = LandContour, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

Utilities: This one is pretty useless since they are all the same
```{r}
ggplot(trialproj, aes(x = Utilities, fill = affordabilitty)) + geom_bar() + facet_wrap(~affordabilitty)
```

LotConfig:
```{r}
ggplot(trialproj, aes(x = LotConfig, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

LandSlope:
```{r}
ggplot(trialproj, aes(x = LandSlope, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

Neighborhood:
```{r}
ggplot(trialproj, aes(x = Neighborhood, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

Condition1:
```{r}
ggplot(trialproj, aes(x = Condition1, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

Condition2:
```{r}
ggplot(fullproj, aes(x = Condition2, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

Building Type:
```{r}
ggplot(trialproj, aes(x = BldgType, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

House Style:

```{r}
ggplot(fullproj, aes(x = HouseStyle, fill = affordabilitty)) + geom_bar(position = position_dodge())
```


Overall ranks:
```{r}
ggplot(fullproj, aes(x = OverallQual, fill = affordabilitty)) + geom_density(alpha = 0.5) #Yes
ggplot(fullproj, aes(x = OverallCond, fill = affordabilitty)) + geom_density(alpha = 0.5) #Not as much

mean(Affordable$OverallCond)
mean(Unaffordable$OverallCond) #Actually slightly lower than the affordable homes

mean(Affordable$OverallQual)
mean(Unaffordable$OverallQual) #However this one is a little more than 2 levels higher

#Confirms results in graph, Qual seems like a good predictor, Cond does not. 

```

Year info:
```{r}
min(YearBuilt);min(YearRemodAdd) #No houses on that haven't been built/remodeled before 1950
ggplot(trialproj, aes(x = YearBuilt, fill = affordabilitty)) + geom_density(alpha = 0.5) #Yes
ggplot(trialproj, aes(x = YearRemodAdd, fill = affordabilitty)) + geom_density(alpha = 0.5) #Yes
ggplot(trialproj, aes(x = YrSold, fill = affordabilitty)) + geom_histogram(position= position_dodge()) #Maybe slightly? But not much
ggplot(trialproj, aes(x = MoSold, fill = affordabilitty)) + geom_density(alpha = 0.5) #No

yearmod <- glm(affordabilitty ~ YearBuilt + YearRemodAdd, data = trialproj, family = 'binomial')
yearmod2 <- glm(affordabilitty ~ MoSold + YrSold, data = trialproj, family = 'binomial')
vif(yearmod2)
```

Roof Style and Material:
```{r}
ggplot(fullproj, aes(x = RoofStyle, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

```{r}
ggplot(trialproj, aes(x = RoofMatl, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

Exterior 1st and 2nd:
```{r}
ggplot(trialproj, aes(x = Exterior1st, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

```{r}
ggplot(trialproj, aes(x = Exterior2nd, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

```{r}
summary(trialproj$Exterior1st)
summary(trialproj$Exterior2nd)
```

```{r}
extmod <- glm(affordabilitty ~ Exterior1st + Exterior2nd, data = trialproj, family = 'binomial')
vif(extmod)
```


Masonry Veneer Type:
```{r}
ggplot(trialproj, aes(x = MasVnrType, fill = affordabilitty)) + geom_bar(position = position_dodge())

trialproj$MasVnrType[1]
trialproj$MasVnrType <- as.factor(trialproj$MasVnrType)

MasYN <- c(length(trialproj$affordabilitty))
for(i in 1:length(trialproj$affordabilitty)){
  if(trialproj$MasVnrType[i] == "BrkCmn"){
    MasYN[i] <- 1
  }
  if(trialproj$MasVnrType[i] == "BrkFace"){
    MasYN[i] <- 1
  }
  if(trialproj$MasVnrType[i] == "Stone"){
    MasYN[i] <- 1
  }
  if(trialproj$MasVnrType[i] == "None"){
    MasYN[i] <- 0
  }
  if(trialproj$MasVnrType[i] == "NA"){
    MasYN[i] <- 0
  }
}
```

```{r}
mastesttype <- which(is.na(new.test$MasVnrType) == TRUE)
```

```{r}
typemod <- glm(affordabilitty ~ MasVnrType, data = trialproj, family = 'binomial')
areamod <- glm(affordabilitty ~ MasVnrArea, data = trialproj, family = 'binomial')
togmod <- glm(affordabilitty ~ MasVnrArea + MasVnrType, data = trialproj, family = 'binomial')
summary(togmod)
vif(togmod)
summary(typemod);summary(areamod)
```


Masonry Veneer Area:
```{r}
ggplot(fullproj, aes(x = MasVnrArea, fill = affordabilitty)) + geom_density(alpha = 0.5) #No
```

Exterior Quality and Condition:
```{r}
ggplot(trialproj, aes(x = ExterQual, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

```{r}
ggplot(trialproj, aes(x = ExterCond, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

Foundation:
```{r}
ggplot(trialproj, aes(x = Foundation, fill = affordabilitty)) + geom_bar(position = position_dodge())
```


Basement Info:

```{r}
ggplot(trialproj, aes(x = BsmtQual, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

```{r}
ggplot(fullproj, aes(x = BsmtCond, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

```{r}
ggplot(trialproj, aes(x = BsmtExposure, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

```{r}
ggplot(trialproj, aes(x = BsmtFinType1, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

```{r}
ggplot(trialproj, aes(x = BsmtFinType2, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

```{r}
ggplot(trialproj, aes(x = BsmtFinSF1, fill = affordabilitty)) + geom_density(alpha = 0.5)
ggplot(trialproj, aes(x = BsmtFinSF2, fill = affordabilitty)) + geom_density(alpha = 0.5)
ggplot(trialproj, aes(x = BsmtUnfSF, fill = affordabilitty)) + geom_density(alpha = 0.5)
ggplot(trialproj, aes(x = TotalBsmtSF, fill = affordabilitty)) + geom_density(alpha = 0.5)

library(car)
bsmtmod <- glm(affordabilitty ~ BsmtFinSF1 + BsmtFinSF2 + BsmtUnfSF + TotalBsmtSF, data = trialproj, family = 'binomial')
vif(bsmtmod)

ggplot(trialproj, aes(x = BsmtFullBath, fill = affordabilitty)) + geom_histogram(position = position_dodge())
ggplot(trialproj, aes(x = BsmtHalfBath, fill = affordabilitty)) + geom_histogram(position = position_dodge())
```

Heating Info:
```{r}
ggplot(trialproj, aes(x = Heating, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

```{r}
ggplot(trialproj, aes(x = HeatingQC, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

Central Air:
```{r}
ggplot(fullproj, aes(x = CentralAir, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

Electrical:
```{r}
ggplot(fullproj, aes(x = Electrical, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

Square Footage Info:
```{r}
ggplot(fullproj, aes(x = X1stFlrSF, fill = affordabilitty)) + geom_density(alpha = 0.5)
ggplot(fullproj, aes(x = X2ndFlrSF, fill = affordabilitty)) + geom_density(alpha = 0.5)
ggplot(fullproj, aes(x = LowQualFinSF, fill = affordabilitty)) + geom_density(alpha = 0.5)
ggplot(fullproj, aes(x = GrLivArea, fill = affordabilitty)) + geom_density(alpha = 0.5)

sfmod <- glm(affordabilitty ~ X1stFlrSF + GrLivArea, data = trialproj, family = 'binomial')
vif(sfmod)
head(trialproj)
```

Full/Half Bath:

```{r}
ggplot(trialproj, aes(x = FullBath, fill = affordabilitty)) + geom_density(alpha = 0.5) #Yes
ggplot(trialproj, aes(x = HalfBath, fill = affordabilitty)) + geom_density(alpha = 0.5) #Yes

bathmod <- glm(affordabilitty ~ FullBath + HalfBath, data = trialproj, family = 'binomial')
vif(bathmod)
```

Above Ground Info:

```{r}
ggplot(trialproj, aes(x = BedroomAbvGr, fill = affordabilitty)) + geom_histogram(position = position_dodge(), binwidth = 1)
ggplot(trialproj, aes(x = KitchenAbvGr, fill = affordabilitty)) + geom_histogram(position = position_dodge(), binwidth = 1)
ggplot(trialproj, aes(x = TotRmsAbvGrd, fill = affordabilitty)) + geom_histogram(position = position_dodge(), binwidth = 1)

abovemod <- glm(affordabilitty ~ BedroomAbvGr + KitchenAbvGr + TotRmsAbvGrd, data = trialproj, family = 'binomial')
summary(abovemod)
```

Kitchen Qual:
```{r}
library(ggplot2)
ggplot(kitchensub, aes(x = KitchenQual)) + geom_bar() 
```

Functional:
```{r}
ggplot(trialproj, aes(x = Functional, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

Fireplaces:

```{r}
ggplot(trialproj, aes(x = Fireplaces, fill = affordabilitty)) + geom_histogram(position = position_dodge())

FireplaceYN <- numeric(length(trialproj$affordabilitty))
for(i in 1:length(trialproj$affordabilitty)){
  if(trialproj$Fireplaces[i] > 0){
    FireplaceYN[i] <- 1
  }
  if(trialproj$Fireplaces[i] == 0){
    FireplaceYN[i] <- 0
  }
}
trialproj$FireplaceYN <- as.factor(FireplaceYN)
ggplot(trialproj, aes(x = FireplaceYN, fill = affordabilitty)) + geom_histogram(stat = 'count', position = position_dodge(), bins = 10) + labs(title = "Fireplace YN by Affordability") + theme(plot.title = element_text(hjust = 0.5))
```

```{r}
ggplot(trialproj, aes(x = FireplaceQu, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

```{r}
ggplot(trialproj, aes(x = FireplaceYN, fill = affordabilitty)) + geom_histogram(position = position_dodge())
```


Garage Info:

```{r}
ggplot(fullproj, aes(x = GarageType, fill = affordabilitty)) + geom_bar() + facet_wrap(~affordabilitty)
```

```{r}
ggplot(fullproj, aes(x = GarageCars, fill = affordabilitty)) + geom_density(alpha = 0.5)
ggplot(fullproj, aes(x = GarageArea, fill = affordabilitty)) + geom_density(alpha = 0.5)
```
```{r}
ggplot(fullproj, aes(x = GarageFinish, fill = affordabilitty)) + geom_bar() + facet_wrap(~affordabilitty)
```
```{r}
ggplot(fullproj, aes(x = GarageQual, fill = affordabilitty)) + geom_bar() + facet_wrap(~affordabilitty)
```
```{r}
ggplot(fullproj, aes(x = GarageCond, fill = affordabilitty)) + geom_bar() + facet_wrap(~affordabilitty)
```

Paved Drive:
```{r}
ggplot(fullproj, aes(x = PavedDrive, fill = affordabilitty)) + geom_bar() + facet_wrap(~affordabilitty)
```


Porch Info:

```{r}
ggplot(trialproj, aes(x = WoodDeckSF, fill = affordabilitty)) + geom_density(alpha = 0.5)
ggplot(trialproj, aes(x = OpenPorchSF, fill = affordabilitty)) + geom_density(alpha = 0.5)
ggplot(trialproj, aes(x = log(EnclosedPorch), fill = affordabilitty)) + geom_density(alpha = 0.5)
ggplot(trialproj, aes(x = X3SsnPorch, fill = affordabilitty)) + geom_density(alpha = 0.5)
ggplot(trialproj, aes(x = ScreenPorch, fill = affordabilitty)) + geom_density(alpha = 0.5)

summary(trialproj[which(trialproj$affordabilitty == "Affordable"),]$EnclosedPorch)
summary(trialproj[which(trialproj$affordabilitty == "Unaffordable"),]$EnclosedPorch)

porchmod <- glm(affordabilitty ~ WoodDeckSF + OpenPorchSF + EnclosedPorch + X3SsnPorch + ScreenPorch, data = trialproj, family = 'binomial')
vif(porchmod)
head(trialproj)

porch <- numeric(length(trialproj$affordabilitty))
for(i in 1:length(trialproj$affordabilitty)){
  if((trialproj$OpenPorchSF[i] | trialproj$EnclosedPorch[i] | trialproj$X3SsnPorch[i] | trialproj$ScreenPorch[i]) > 0)
    porch[i] = "Porch"
  if((trialproj$OpenPorchSF[i] | trialproj$EnclosedPorch[i] | trialproj$X3SsnPorch[i] | trialproj$ScreenPorch[i]) == 0)
    porch[i] = "No Porch"
}
head(porch)
trialproj <- data.frame(trialproj, porch)
names(trialproj)[81] = "Porch"
head(trialproj)
ggplot(trialproj, aes(x = Porch, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

```{r}
ggplot(trialproj, aes(x = Porch, fill = affordabilitty)) + geom_bar(position = position_dodge())
```


Pool:

```{r}
ggplot(trialproj, aes(x = log(PoolArea), fill = affordabilitty)) + geom_density(alpha = 0.5)
```


```{r}
ggplot(trialproj, aes(x = PoolQC, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

```{r}
head(new.test)
```


Fence Quality:
```{r}
ggplot(fullproj, aes(x = Fence, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

Misc:
```{r}
ggplot(trialproj, aes(x = MiscFeature, fill = affordabilitty)) + geom_bar(position = position_dodge())
```

```{r}
ggplot(trialproj, aes(x = MiscVal, fill = affordabilitty)) + geom_density(alpha = 0.5)
```

Sale info:
```{r}
ggplot(fullproj, aes(x = SaleType, fill = affordabilitty)) + geom_bar() + facet_wrap(~affordabilitty)
```

```{r}
ggplot(fullproj, aes(x = SaleCondition, fill = affordabilitty)) + geom_bar() + facet_wrap(~affordabilitty)
```

